Indirect Conflicts: An Exploration and Discussion of Tools, Process, and Developer Insight

### 2013-08-27 iced-2013/paper.tex
ICED
Up to RQ7 are now inserted into the paper.

\begin{description}[topsep=6pt]
	\item[RQ3] \textit{What software artifacts are susceptible to indirect conflicts?}
\end{description}

@@

@@

\begin{description}[topsep=6pt]
	\item[RQ4] \textit{How do developers react to and solve indirect conflicts?}
\end{description}

% Here use anything they said for tools and process

\begin{description}[topsep=6pt]
	\item[RQ5] \textit{Who is responsible for fixing indirect conflict issues?}
\end{description}

\begin{description}[topsep=6pt]
	\item[RQ6] \textit{Who is responsible for fixing indirect conflict issues?}
\end{description}

@@

\begin{description}[topsep=6pt]
	\item[RQ7] \textit{When are pre-emptive indirect conflict tools best used and what would developers want from them?}
\end{description}

\begin{description}[topsep=6pt]
	\item[RQ8] \textit{When are reactionary indirect conflict tools best used and what would developers want from them?}
\end{description}

>>>>

\begin{description}[topsep=6pt]
	\item[RQ3] \textit{What software artifacts and environments are susceptible to indirect conflicts?}
\end{description}

@@

As per environments, Table~\ref{tab:env} shows which development team environment developers believe to be the most
prone to indirect conflicts.

\begin{table*}[tb!]
\begin{center}
\begin{tabular}{| p{7cm} | c | c | c | c | c |}
\hline
Environment of conflicts & Strongly Disagree & Disagree & Neutral & Agree & Strongly Agree \\
\hline
\hline
Developing alone (conflicts in own code) & 18\% & 20\% & 19\% & 24\% & 19\% \\ \hline
Developing in a team between 2 - 5 developers (Inter-developers conflicts) & 3\% & 8\% & 22\% & 49\% & 18\% \\ \hline
Developing in a multi team environment (Inter-team conflicts) & 1\% & 11\% & 14\% & 39\% & 35\% \\ \hline
\end{tabular}
\end{center}
\caption{Results of survey questions to development environments in which indirect conflicts are likely to occur, in terms of percentage
of developers surveyed.\label{tab:env}}
\end{table*}

@@

\begin{description}[topsep=6pt]
	\item[RQ4] \textit{How do developers catch indirect conflicts?}
\end{description}

Of the 19 developers interviewed, 69\% mentioned forms of testing (unit, integration, etc) as the major component of catching indirect
conflict issues, subscribing to the idea of ``run the regression and integration tests and just see if anything breaks''. 31\% of developers 
said build processes (either nightly builds or building the project themselves), and others mentioned code reviews
while those dealing with a user interface mentioned user complaints from run time testing.

Of the 78 developers survey, 49\% mentioned forms of testing as the major tool used to catch indirect conflicts, 33\% said build processes,
while 31\% used work their IDE or IDE plugins to catch indirect conflicts. Other developers surveyed also mention code review process (14\%)
and project expertise (6\%) as factors of catching indirect conflicts.

\begin{description}[topsep=6pt]
	\item[RQ5] \textit{How to developers react to and solve indirect conflicts?}
\end{description}

Once an indirect conflict has occurred, usually alerted to the developer by test or build failures, 75\% of developers interviewed said
they checked historical logs to help narrow down where the problem could originate from. Most developers had the mindset of
``Look at the change log and see what could possibly be breaking the feature.''. The log most commonly referred to was the source
code change log to see what code has been changed, followed by build failure or test failure logs to examine errors messages and get time 
frames of when events occurred. Developers also mentioned their personal expertise in the project as a large component of solving indirect
conflicts as well as issue or work item trackers as many tests and builds can be linked to these management tools.

Of the developers surveyed, 37\% confirmed that they used some type of source control management tools to help them solve their indirect
conflicts while 23\% said they used native IDE tools and 21\% said they use features of the language's compiler and debugger in order
to solve indirect conflicts. Interestingly, only 13\% of developers mentioned a form of communication with other developers in aid to
solving these conflicts and only 4\% mentioned the reading of formal documentation.

@@

\begin{description}[topsep=6pt]
	\item[RQ6] \textit{When are pre-emptive indirect conflict tools best used and what would developers want from them?}
\end{description}

The developers who were interviewed had a major concern with any pre-emptive tool in that the amount of false positives
provided by the tool may render the tool useless. Developers said ``this could relate to information overload'', ``this would
be a real challenge with the number of dependencies'', ``I only want to know if it will break me'', and ``it depends on how
good the results are in regards to false positives''. These concerns combined with RQ2 suggest that pre-emptive tools are
best used in unstable phases on the project when indirect conflicts are more likely to happen, thus reducing the number of false
positives. One developer in particular noted ``You will spend all your time getting notified and reviewing instead of implementing''.
Interviewed developers also suggested that their proper software development process are already in place to
catch potential issues before they arise such as code review, individual knowledge, IDE call hierarchies (static language analysis),
or communication within the project.

As per what developers would want from such pre-emptive tools, Table~\ref{tab:pre} shows how developers feel towards being 
alerted in certain types of functional changes within code which they are using.

\begin{table*}[tb!]
\begin{center}
\begin{tabular}{| p{7cm} | c | c | c | c | c |}
\hline
Code change type &Never  & Occasionally & Most Times & Always & I Don't Care \\
\hline
\hline
Method signature change & 5\% & 8\% & 12\% & 68\% & 7\% \\ \hline
Pre-condition change & 5\% & 27\% & 37\% & 23\% & 7\% \\ \hline
Main algorithm change & 11\% & 45\% & 19\% & 15\% & 11\% \\ \hline
User interface change & 12\% & 32\% & 20\% & 27\% & 9\% \\ \hline
Run time change & 13\% & 29\% & 25\% & 20\% & 12\% \\ \hline
Post-condition change & 7\% & 28\% & 32\% & 23\% & 11\% \\ \hline
\end{tabular}
\end{center}
\caption{Results of survey questions to source code changes that developers deem notification worthy, in terms of percentage
of developers surveyed.\label{tab:pre}}
\end{table*}

\begin{description}[topsep=6pt]
	\item[RQ7] \textit{When are reactionary indirect conflict tools best used and what would developers want from them?}
\end{description}
